A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-18 text/introduction.tex
Fix the latter half of introduction.

\subsection{Dependent Types}

% \subsubsection{依存型とは何か?}

Dependent types are types which is \AI{are} dependent on values.
We can use dependent types for securer programming. \AI{Cite Xi--Pfenning, for example?}
For example, we can realize vectors with their sizes with them.
\begin{verbatim}
        Vector :: Int -> *
\end{verbatim}
\verb|Vector| is a type constructor which takes the length of vectors, that is, 
\verb|Vector 3| is a type for vectors whose lengths are 3.
If \verb|vadd| function has the type of \verb|Vector n -> Vector n -> Vector n| for any positive number \verb|n|,
we can confirm the two arguments of \verb|vadd| function has the same length.
\red{secure programming? finer grained typing? とか}

\subsection{Multi-stage Programming with Dependent Types}
\red{このsubsectionは短いので上とくっつけてもいいかもしれない}
\AI{くっつけましょう。Section 1 で指摘した問題を依存型で解決するというのは自然なアイデアだし。One natural idea to address this problem is the introduction of dependent types. みたいなこといって、依存型の導入をする。先行研究として Brady--Hammond にもふれる。}
% \subsubsection{「生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
% このため、間違って組み合わせると容易にエラーを引き起こす。」問題を依存型で解決する。}

@@

In this paper, we design a new multi-stage calculus \LMD by 
merging dependent types into existing multi-stage calculus \LTP\cite{Hanada2014}.
\LMD is multi-stage calculus which contains dependent types.
\LMD makes multi-stage programming more safer \AI{remove ``more''} with the power of dependent types.

\AI{Give a summary of our technical contribution as itemization.}

>>>>

\subsection{Multi-stage Programming with Dependent Types}

% 依存型とは何か?

One natural idea to address this problem is the introduction of dependent types.
Dependent types are types which are dependent on values.
We can use dependent types for securer programming like Xi and Pfenning \cite{Xi98}.
For example, we can realize vectors with their sizes with them.
\begin{verbatim}
        Vector :: Int -> *
\end{verbatim}
\verb|Vector| is a type constructor which takes the length of vectors, that is, 
\verb|Vector 3| is a type for vectors whose lengths are 3.
If \verb|vadd| function has the type of \verb|Vector n -> Vector n -> Vector n| for any positive number \verb|n|,
we can confirm the two arguments of \verb|vadd| function has the same length.
% \red{secure programming? finer grained typing? とか}

@@

In this paper, we design a new multi-stage calculus \LMD by 
merging dependent types into existing multi-stage calculus \LTP\cite{Hanada2014}.
\LMD is multi-stage calculus which contains dependent types.
\LMD makes multi-stage programming safer with the power of dependent types.
Our technical contribution are summarized as follows:
\begin{itemize}
        \item we give the formal definition of \LMD with its syntax, 
        type system which contains type equivalence, full, reduction, and staged reduction;
        \item for the full reduction, we prove subject reduction, strong normalization, and confluence
        \item fot the staged reduction, we prove unique decomposition and progress.
\end{itemize}
